Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-14 paper/uist_2016/paper.tex
shorten a related work section, and
change some instances of "GPS" to "geolocation"

Another project by de Silva and Aizawa has also relied on geolocation data to provide a visual examination of interested traveling routes by linking geo-tagging metadata with online imageries, specifically Google Street View images \cite{deSilva:2009:RMT:1631272.1631414}. The authors proposed a sketch-based interface that would perform spatial and temporal queries on line drawings specified by the users. Rewind resembles this interactive system, in a way that the reconstructed sceneries are of a careful mapping results from GPS data and Google Street View images. However, Rewind differs in that the mapping is finalized with GPS data provided by lifeloggers tracked using smartphones. This means that Rewind serves more of a getaway for recalling episodic memory rather than reviewing a potential travelling itinerary, aiming to provide a mechanism for reminiscence and sharing of past experience while exploring lifeloggers' behavioral patterns. Moreover, the reconstruction techniques used in Rewind would differentiate the same retrieved image with various temporal cues such as changes in seasons; yet the immediate results from the temporal queries suggested by de Silva and Aizawa have not been fully revealed.

Other research has used location history not to create a new interface for the user, but for other applications. Neuhaus's UrbanDiary project \cite{neuhaus2010urbandiary} uses GPS devices to create and visualize ``personal tracks'' as well as collective tracks for a city. These personal tracks are created using data from time and location tracking for each trip by each individual. The researchers focused on comparing the different visualization techniques used to portray the data. A two-month study involved twenty participants wearing GPS devices, but as the paper was published in 2010, they did not use smartphone GPS data. Each participant wore a device, and the paper suggests that doing so helped them feel in charge of the data collection. Furthermore, GPS tracking is noted as a good method for collecting data about movement of each person. Using geotagged images from Flickr, Becker et al's work has shown that movement trajactories in metropolian areas tend to converge at Points of Interests(POIs) \cite{Becker2015}. As noted, a further exploration of these projects could be investigating what participants' perceptions were while moving. The data from these studies show each person's location data can be used as a unique fingerprint. This supports the idea that location data can be used to help people recreate their individual travel experiences, for purposes of reminiscing and even sharing. In a similar vein, Cranshaw et al. \cite{cranshaw2012livehoods} recognize the ability for collective location data to understand the social patterns in a city. That everyone travels their own path, and this is part of their identity, is a core theme in Rewind.

Further work in GPS user behavior has been done by Leshed et al. to see how users interpret and interact with spaces differently when using in-car GPS navigation \cite{leshed2008car}. They found that ``the GPS disconnects the drivers from the external environment.'' As a result of the drivers' disengagement with their surroundings, ``the process of interpreting the world, adding value to it, and turning space into place is reduced to a certain extent and drivers remain detached from the indifferent environments that surround them.'' Since Rewind touches on the topic of travel, it also inherently deals with car travel and GPS. We imagine that regular GPS users will interact with Rewinds differently.

@@

\section{The Rewind System}
\textit{Rewind} recreats the visual sensation of travelling down past routes using raw Google Location History data retrieved by lifeloggers. Differing from previously studied hyperlapse creation techniques by Kopft et al. and Joshi et al \cite{opf:2014:FHV:2601097.2601195, Joshi:2015:RHC:2809654.2766954}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight. \textit{Rewind} inputs lifeloggers' geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images. The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues. \textit{Rewind} is a client-side only application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store it.

@@

For each photo-Rewind pair, the participant was first shown a photo of one of the locations found in their GPS data. The participant was asked to answer the following questions about the photo:

>>>>

Another project by de Silva and Aizawa has also relied on geolocation data to provide a visual examination of interested traveling routes by linking geo-tagging metadata with online imageries, specifically Google Street View images \cite{deSilva:2009:RMT:1631272.1631414}. The authors proposed a sketch-based interface that would perform spatial and temporal queries on line drawings specified by the users. Rewind resembles this interactive system, in a way that the reconstructed sceneries are of a careful mapping results from geolocation data and Google Street View images. However, Rewind differs in that the mapping is finalized with geolocation data provided by lifeloggers tracked using smartphones. This means that Rewind serves more of a getaway for recalling episodic memory rather than reviewing a potential travelling itinerary, aiming to provide a mechanism for reminiscence and sharing of past experience while exploring lifeloggers' behavioral patterns. Moreover, the reconstruction techniques used in Rewind would differentiate the same retrieved image with various temporal cues such as changes in seasons; yet the immediate results from the temporal queries suggested by de Silva and Aizawa have not been fully revealed.

Other research has used location history not to create a new interface for the user, but for other applications. Neuhaus's UrbanDiary project \cite{neuhaus2010urbandiary} uses GPS devices to create and visualize ``personal tracks'' as well as collective tracks for a city. These personal tracks are created using data from time and location tracking for each trip by each individual. The researchers focused on comparing the different visualization techniques used to portray data from a two-month study involved twenty participants wearing GPS devices. Using geotagged images from Flickr, Becker et al.'s work has shown that movement trajactories in metropolian areas tend to converge at Points of Interests(POIs) \cite{Becker2015}. The data from these studies show each person's location data can be used as a unique fingerprint. This supports the idea that location data can be used to help people recreate their individual travel experiences, for purposes of reminiscing and even sharing. In a similar vein, Cranshaw et al. \cite{cranshaw2012livehoods} recognize the ability for collective location data to understand the social patterns in a city. That everyone travels their own path, and this is part of their identity, is a core theme in Rewind.

Further work in location-based user behavior has been done by Leshed et al. to see how users interpret and interact with spaces differently when using in-car GPS navigation \cite{leshed2008car}. They found that ``the GPS disconnects the drivers from the external environment.'' As a result of the drivers' disengagement with their surroundings, ``the process of interpreting the world, adding value to it, and turning space into place is reduced to a certain extent and drivers remain detached from the indifferent environments that surround them.'' Since Rewind touches on the topic of travel, it also inherently deals with car travel and GPS. We imagine that regular GPS users will interact with Rewinds differently.

@@

\section{The Rewind System}
\textit{Rewind} recreates the visual sensation of travelling down past routes using raw Google Location History data retrieved by lifeloggers. Differing from previously studied hyperlapse creation techniques by Kopft et al. and Joshi et al \cite{opf:2014:FHV:2601097.2601195, Joshi:2015:RHC:2809654.2766954}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight. \textit{Rewind} is a web interface that receives lifeloggers' geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images. The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues. \textit{Rewind} is a client-side only application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store it.

@@

For each photo-Rewind pair, the participant was first shown a photo of one of the locations found in their geolocation data. The participant was asked to answer the following questions about the photo:
